\SW: II. Did we beat the lens finding robots in CFHTLS?

### 2014-09-08 doc/sw-cfhtls.tex
Defined RF sample in paper, numbers in Gavazzi et al don't match those from SQL queries, emailing RG. #69

\subsection{Known \cfhtls lens samples}
\label{sec:data:kls}

The \cfhtls data has been searched for lenses using semi-automated
algorithms, primarily, in the $g$ band which is optimal for finding
lenses. Here, we briefly mention the lens samples which were known to
the authors prior to the lens search with \sw.

At galaxy-scales, there are two main types of lens searches. The
RingFinder \citet{Gavazzi2014} was used for finding compact rings or arcs
around centers of isolated and massive early-type galaxies. By
subtracting the PSF-matched i-band images from the g-band, the
algorithm looks for excess flux in the bluer g-band which is typical of
the distant lensed star forming galaxies. An object detector measures
the properties of these residual blue features and candidates meeting a
length-width ratio and tangential alignment criteria are then visually
inspected to form the final sample. This rings sample consists of 39
confirmed lenses and 17 promising candidates.

@@

For the purpose of transparency, the volunteers participating in
\sw-\cfhtls lens search were made aware of these known lens samples. Images
containing the lenses from these lens samples were labelled so in the
forum Talk where volunteers have the opportunity to discuss their
findings with other volunteers and the science team.

>>>>

\subsection{Existing \cfhtls lens samples}
\label{sec:data:kls}

The \cfhtls data has been searched for lenses using semi-automated algorithms,
primarily, in the $g$ band where the predominantly  faint blue  source
galaxies are bright compared to the predominantly red deflector galaxies.
Here, we briefly mention the lens samples which were known to the authors
prior to the lens search with \sw.

At galaxy-scales, we focus on two primary lens searches. The RingFinder
\citep{Gavazzi2014} was used for finding compact rings or arcs around centers
of isolated and massive early-type galaxies. By subtracting the PSF-matched
$i$-band images from the $g$-band images, the algorithm looks for excess flux
in the bluer $g$-band. An object detector measures the properties of these
residual blue features, and candidates meeting length-width ratio and
tangential alignment criteria are then visually inspected to form the final
sample. \citet{Gavazzi2014} first selected some 638,000 targets as either
photometrically-classified early type galaxies, or objects selected to have
red centers and blue outer parts. 14370 were found to show detectable blue
residuals, and 2524 were visually inspected, having passed the automatic
feature selection process. This led to a sample of 42 good quality
(\texttt{q\_flag} = 3) and 288 medium quality (\texttt{q\_flag} = 2) lens
candidates. In addition to this well defined sample, \citet{Gavazzi2014}
reported a further 71 serendipitously detected lens candidates. 
From this sample of ``RingFinder candidates,'' the SL2S team found, during
their follow-up campaign, 39 confirmed lenses (and 17 promising
candidates). We use this sample of 39 ``confirmed RingFinder lenses'' in our
completeness analysis.

\todo{Phil}{check with RG about SQL queries for the RF candidates.
\texttt{q\_flag = 3} returns 55, not 42, systems, and 
\texttt{q\_flag = 3} returns 346, not 288, systems. This is all issue \#69}

@@

For the purposes of transparency and to help a little with their training, 
the volunteers participating in \sw-\cfhtls lens search were made aware of
these known lens samples. Images containing the systems from the above samples
were labelled as ``Known Lens Candidates'' in the Talk forum, where volunteers
have the opportunity to discuss their findings with other volunteers and the
science team.
